---
title: "Automated Stock Trading with R"
author: "W. Claster"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Setup

I use the following API’s
Google Cloud Platform
Robinhood
Yahoo Finance

To create the pipeline, I used the R Markdown document. I use these libraries to manipulate financial data.

```{r cars}
library(dplyr)
library(purrr)
library(dbplyr)
```
RobinHood library interacts with Robinhood accounts. Quantmod library allows to interact with yahoo finance data and includes useful libraries for technical analysis.
```
library(RobinHood)
library(quantmod)
```
I use googlesheets4, big query and DBI to interact with databases, which are based on Google Cloud services.

```
library(googlesheets4)
library(bigrquery)
library(DBI)
```
The library here is used to access local R scripts with defined functions

library(here)
source(here("src", "R", "data_functions.R"))
source(here("src", "R", "trading_models.R"))```

```


## 2. Connecting API’s

I set the billing to my project and make a connection with Google’s API using .json file.

```{r auth, echo=FALSE}

gs4_auth(
path = "google_auth.json",
cache = FALSE
)
```
Inside .Rprofile I set the following variables for sys environment.
# Put that inside .Rprofile system file
Sys.setenv("username" = "adam")
Sys.setenv("password" = "test")
And then make a connection with RobinHood API’s. .Rprofile file passes relevant credentials defined above.

##3. Gathering data and making decision
I then gather all relevant data using Yahoo Finance API.

```
# This function is located in data_functions.R script
get_market_data <- function() {
 # Load data into the workspace
 getSymbols("AAPL", src="yahoo")
 return(AAPL)
}
data <- get_market_data()
```
